---
title: "TBSFrugivoreTraits"
author: "J Ballantyne"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1 EltonTraits - Mammals
#2 EltonTraits - Birds
#3 Pantheria test and missing data added - Mammals
#4 AVOnet - Birds

#1 EltonTraits - Mammals (My try for the mammals with elton_mammals in the package "traitdata")
## Get packages
```{r}
if(!require(dplyr))install.packages("dplyr", dependencies = TRUE)
if(!require(devtools))install.packages("devtools", dependencies = TRUE)
if(!require(traitdata))install.packages("traitdata", dependencies = TRUE)
if(!require(tidyr))install.packages("tidyr", dependencies = TRUE)
```
## Load packages
```{r}
library(dplyr)
library(devtools)
library(traitdata)
library(tidyr)
```
## Check out elton_mammals
```{r}
##traitdata::elton_mammals
```
## Load Tiputini species list data - file is 082924_animals2.csv
```{r}
TBS_animals1 <- read.csv("/Users/jacquelineballantyne/Desktop/R_2024/TCTS_data/082924_animals2.csv", header=T, as.is=T)
```
## Remove volant mammals (for now)
```{r}
TBS_mams <- TBS_animals1[TBS_animals1$Class == "Mammalia", ]

TBS_nonvolmams <- TBS_mams[TBS_mams$Order != "Chiroptera", ]
```
## Get rid of silly cols in Tiputini data
```{r}
keeplist <- c("Scientific_name", "Common_name", "IUCN" #,"Detected"
              )
TBS_nonvolmams1 <- TBS_nonvolmams[,keeplist]
```
## Load elton_mammals database
```{r}
data("elton_mammals")
elton_mams1 <- elton_mammals
elton_mams1$Scientific_name <- paste(elton_mams1$Genus, elton_mams1$Species, sep = " ")
```
## Get traits and headers
```{r}
names(elton_mams1)
names(TBS_nonvolmams1)
```

## Remove undetected mammals (do this step when you get the final list)
```{r}
###TBS_nonvolmams_detected <- TBS_animals2[TBS_animals2$Detected == "Yes", ]
```

## elton_mams species with traits (do this once I have selected the traits to keep)
```{r}
#keeplist <- c("Scientific_name", "AdultBodyMass_g") ## I think I should just skip this step and see if it works then go back and just keep ones that are complete for my list or nearly so

#elton_mams2 <- elton_mams1[,keeplist]
```
## merging my list with the elton_mammals list to get traits for mine only
```{r}
head(elton_mams1)
TBS_nonvolmams_elton <- merge(TBS_nonvolmams, elton_mams1, by.x = "Scientific_name", by.y = "Scientific_name", all.x = T, all.y = F)
head(TBS_nonvolmams_elton) 
```
## show the ones that dont match
```{r}
TBS_nonvolmams_elton_noNA <- na.omit(TBS_nonvolmams_elton)
```

```{r}
TBS_nonvolmams_nonmatch <- anti_join(TBS_nonvolmams_elton, TBS_nonvolmams_elton_noNA, by="Scientific_name")
head(TBS_nonvolmams_nonmatch)
```

### Notes from ^
#### I made two columns in my data set with the most up to date Scientific name and the old names used in elton_traits - I remember seeing a code somewhere that auto updated but I dont have time for that rn


```{r}
##summary(traitdata)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
